A survey of IND-CCA constructions

### 2024-04-17 co789/project/manuscript/main.tex
project checkpoint

% Algorithms and pseudocode
\usepackage{algorithm}
\usepackage{algpseudocode}

% Common shortcuts
\newcommand{\round}[1]{\lfloor {#1} \rceil}
\newcommand{\norm}[1]{\Vert {#1} \Vert}
\newcommand{\var}[1]{\operatorname{Var}[{#1}]}
\newcommand{\leftsample}{\overset{{\scriptscriptstyle\$}}{\leftarrow}}

% Environments: definitions, theorems, propositions, corollaries, lemmas
%    Theorems, propositions, and definitions are numbered within the section
%    Corollaries are numbered within the theorem, though they are rarely used
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{remark}{Remark}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[theorem]

@@

\section{The Fujisaki-Okamoto Transformation}
The Fujisaki-Okamoto transformation \cite{fujisaki1999secure} takes a IND-CPA public-key encryption scheme (PKE) and a few other cryptographic primitives of weaker security as inputs, and constructs a hybrid encryption scheme that achieves IND-CCA2 security.

In the conference paper, the security reduction is performed under the random oracle model, and the security of the hybrid scheme degrades linearly with the number of hash queries and the number of decryption queries. On the other hand, this scheme is desirable for its simplicity, and the low requirements for the input primitives: the PKE only needs to be one-time one-way secure, and the symetric cipher only needs to be indistinguishable under one-time attack.

% TODO: Need more introduction?

\subsection{The hybrid scheme and security result}
The hybrid encryption scheme contains three routines: key generation, encryption, and decryption. The input for the hybrid scheme includes a public-key encryption scheme $\text{KeyGen}^\text{asym}, E^\text{asym}, D^\text{asym}$, a symmetric encryption scheme $E^\text{sym}, D^\text{sym}$, and two hash functions $G: \mathcal{M}^\text{asym} \mapsto \mathcal{K}^\text{sym}, H: \mathcal{M}^\text{asym} \times \mathcal{C}^\text{sym} \mapsto \text{Coin}^\text{asym}$.

\begin{algorithm}
\caption{FO Key generation}\label{fo-key-gen}
\begin{algorithmic}[1]  % [1] is for displaying line number
    \State $
        (\text{PK}^\text{asym}, \text{SK}^\text{asym}) 
        \leftarrow \text{PKE.KeyGen}()
    $
    \State $
        \text{PK}^\text{hy} \leftarrow \text{PK}^\text{asym},
        \text{SK}^\text{hy} \leftarrow \text{SK}^\text{asym},
    $

    \State \Return $(\text{PK}^\text{hy}, \text{SK}^\text{hy})$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{FO Key encryption}\label{fo-key-enc}
\begin{algorithmic}[1]  % [1] is for displaying line number
    \Require $m \in \mathcal{M}^\text{sym}$
    \State Sample from the PKE's message space $\sigma \leftsample \mathcal{M}^\text{asym}$
    \State $a \leftarrow G(\sigma)$, $c \leftarrow E^\text{sym}_a(m)$
    \State $h \leftarrow H(\sigma, c)$
    \State $e \leftarrow E^\text{asym}(\text{PK}^\text{hy}, \sigma, h)$

    \State \Return $(e, c)$
\end{algorithmic}
\end{algorithm}

\pagebreak

The decryption routine:

\begin{algorithm}
\caption{FO Key decryption}\label{fo-key-dec}
\begin{algorithmic}[1]  % [1] is for displaying line number
    \Require The ciphertext $(e, c)$

    \State $
        \hat{\sigma} \leftarrow D^\text{asym}(\text{SK}^\text{hy}, e)
    $

    \State $
        \hat{h} \leftarrow H(\hat{\sigma}, c)
    $

    \State $
        \hat{e} \leftarrow E^\text{asym}(\text{PK}^\text{hy})
    $

    \If{$\hat{e} \neq e$}
        \State \Return $\bot$
    \EndIf

    \State $\hat{a} \leftarrow G(\hat{\sigma})$
    \State $\hat{m} \leftarrow D^\text{sym}_{\hat{a}}(c)$
    \State \Return $\hat{m}$
\end{algorithmic}
\end{algorithm}

\begin{theorem}\label{fo-security-theorem}
    For all IND-CCA adversary $\mathcal{A}^\text{hy}$ against the hybrid encryption scheme with advantage $\epsilon^\text{hy}$, there exists a one-way one-time-encryption adversary against the public-key encryption scheme with advantage $\epsilon^\text{asym}$ and an one-time indistinguishability adversary against the symmetric encryption scheme with advantage $\epsilon^\text{sym}$ such that

    \begin{equation*}
        \epsilon^\text{hy} \leq q_\text{H}\epsilon^\text{asym} + \epsilon^\text{sym} + q_\text{D}2^{-\gamma}
    \end{equation*}

    where $\gamma$ is the spread of the public-key encryption scheme, $q_\text{H}$ is the total number of hash queries, and $q_\text{D}$ is the total number of decryption queries
\end{theorem}

\subsection{Proof of security result}
Theorem \ref{fo-security-theorem} is proved using a sequence of games that involves $\mathcal{A}^\text{hy}$ as the main routine, and two games that involves $\mathcal{A}^\text{hy}$ as a sub-routine. The sequence of games is as follows:

\begin{itemize}
    \item Game 0 is the standard IND-CCA2 game

    \item Game 1 is identical to game 0, except that the decryption oracle $\mathcal{O}_D$ is modified. Instead of using the true secret key $\text{SK}^\text{hy}$ to decrypt the query $(e_q, c_q)$, the decryption oracle checks the tape of hash function $H$ for the existence of hash query $(\sigma_H, c_H, h_H)$ such that $c_q = c_H$ and $e_q = E^\text{asym}(\text{PK}^\text{asym}, \sigma_H, h_H)$. If such a query exists, then $\mathcal{O}_D$ uses $\sigma_H$ to derive the symmetric key $a_q \leftarrow G(\sigma_H)$ and decrypt the queried ciphertext $c_q$. If no such query exists, then $\mathcal{O}_D$ will reject the queried ciphertext and output a decryption error. It is worth noting that this modified decryption oracle does not require the hybrid secret key $\text{SK}^\text{hy}$ to process decryption queries.

    \item Game 2 is identical to game 1, except the routine of encrypting the challenge ciphertext is modified: $a^\ast \leftsample \mathcal{K}^\text{sym}$ is randomly sampled from the symmetric key space instead of being queried from $G$, and $h^\ast \leftsample \text{COIN}^\text{asym}$ is randomly sampled from the asymmetric coin space instead of being queried from $H$.
\end{itemize}

Let $S_0, S_1, S_2$ denote the event that $\mathcal{A}^\text{hy}$ wins game 0, game 1, and game 2, respectively.

\begin{lemma}\label{fo-win0-win1}
    Let $q_D$ denote the number of decryption queries, and $\gamma$ denote the spread of the PKE, then
    \begin{equation*}
        P[S_0] - P[S_1] \leq q_D 2^{-\gamma}
    \end{equation*}
\end{lemma}

\begin{proof}
    For each decryption query $(e_q, c_q)$, there are three mutually exclusive possibilities:

    \begin{enumerate}
        \item The queried ciphertext is \textbf{honest}, meaning that there is a matching record on the tape of the hash function $H$
        \item There is no matching record on the tape of the hash function $H$, and the check in step 4 in algorithm \ref{fo-key-dec} will fail, outputing decryption error. Such a query is called \textbf{invalid}
        \item There is no matching record on the tape of the hash function $H$, but the check in step 4 of algorithm \ref{fo-key-dec} will succeed. Such a query is called \textbf{almost valid}
    \end{enumerate}

    Observe that for both $S_0, S_1$:

    $$
    \begin{aligned}
        P[S] &= P[S \cap \text{ all decryption queries are honest }] \\
        &+ P[S \cap \text{ some decryption queries are dishonest, but none is almost valid }] \\
        &+ P[S \cap \text{ at least one almost valid decryption queries }]
    \end{aligned}
    $$

    When all decryption queries are honest, the decryption oracles will correctly decrypt the query in both game 0 and game 1. When all dishonest decryption queries are invalid, the decryption oracles will reject the query in both games. The only difference between the two games lies in how the decryption oracle processes almost valid decryption queries. Therefore:

    $$
    \begin{aligned}
        &P[S_0] - P[S_1] \\
        &= P[S_0 \cap \text{ at least one almost valid decryption queries }] \\
        &- P[S_1 \cap \text{ at least one almost valid decryption queries }] \\
        &\leq P[\text{ at least one almost valid decryption queries }]
    \end{aligned}
    $$

    Let $(e, c)$ be some decryption query made without querying $H$, then in the true decryption routine, $\hat{h} \leftarrow H(\hat{\sigma}, c)$ will be a truly random coin, and $\hat{e} \leftarrow E^\text{asym}(\hat{\sigma}, \hat{h})$ will be a truly random ciphertext for the given public key and $\hat{\sigma}$. Since the the PKE has $\gamma$ spread, we know that $P[e = \hat{e}] = P[(e, c) \text{ is almost valid}] \leq 2^{-\gamma}$. Among $q_D$ decryption query, the probability of having at least one almost valid query is bounded by sum of probability of each decryption query being almost valid: $P[\text{ at least one almost valid query }] \leq q_D 2^{-\gamma}$.
\end{proof}

If during the IND-CCA game, $\mathcal{A}^\text{hy}_\text{IND-CCA}$ never makes hash query that involves $\sigma^\ast$, then under the random oracle model, there is no difference between sampling $a^\ast, h^\ast$ randomly or pseudorandomly. On the other hand, if the adversary does make such a query, then there is an inconsistency between the challenge ciphertext and the results of such hash query. In other words, the difference between game 1 and game 2 is the even that the IND-CCA adversary makes such a hash query:

\begin{lemma}
    $$
    P[S_1] - P[S_2] = P[\text{query}]
    $$
\end{lemma}

Denote the challenge ciphertext in game 2 by $(e^\ast, c^\ast)$. Notice that $e^\ast$ is the encryption of a truly random $\sigma^\ast$ using a truly random coin $h^\ast$, while $c^\ast$ is the encryption of $m_b^\ast$ under a truly random key $a^\ast$. This allows a OW-CPA game for the PKE, and an IND-CPA game for the symmetric cipher to be perfectly simulated by some $\mathcal{A}^\text{asym}_\text{OW-CPA}$ and/or $\mathcal{A}^\text{sym}_\text{IND-CPA}$. Using this strategy, we can bound $P[S_2]$ and $P[\text{query}]$ using the advantage of some OW-CPA and/or IND-CPA adversaries.

\begin{lemma}\label{fo-bound-s2}
    For every IND-CCA adversary $A^\text{hy}_\text{IND-CCA}$, there exists an IND-OTE adversary against the underlying symmetric cipher $\mathcal{A}^\text{sym}_\text{IND-OTE}$ with advantage $\epsilon^\text{sym}_\text{IND-OTE}$ such that

    $$
    P[S_2] = \frac{1}{2} + \epsilon^\text{sym}_\text{IND-OTE}
    $$
\end{lemma}

\begin{proof}
    $\mathcal{A}^\text{sym}_\text{IND-OTE}$ can perfectly simulate the hybrid key generation $\text{PK}^\text{hy} = \text{PK}^\text{asym}, \text{SK}^\text{hy} = \text{SK}^\text{asym}$, the random oracles $G, H$, as well as the modified decryption oracle.

    When $\mathcal{A}^\text{hy}_\text{IND-CCA}$ submits the challenge plaintexts $(m_0, m_1)$, $\mathcal{A}^\text{sym}_\text{IND-OTE}$ passes them to the symmetric cipher challenger and receives the symmetric challenge ciphertext $c^\ast$. $\mathcal{A}^\text{sym}_\text{IND-OTE}$ then randomly samples $\sigma^\ast \leftsample \mathcal{M}^\text{asym}$ and $h^\ast \leftsample \text{COIN}^\text{asym}$ and computes $e^\ast \leftarrow E^\text{asym}(\text{PK}^\text{asym}, \sigma^\ast, h^\ast)$. $(e^\ast, c^\ast)$ is given to $\mathcal{A}^\text{hy}_\text{IND-CCA}$ as the challenge ciphertext. It is easy to verify that from $\mathcal{A}^\text{hy}_\text{IND-CCA}$'s perspective, this game is exactly game 2; in addition $\mathcal{A}^\text{hy}_\text{IND-CCA}$ wins the game if and only if $\mathcal{A}^\text{sym}_\text{IND-OTE}$ wins the game.
\end{proof}

\begin{lemma}
    For every IND-CCA adversray $\mathcal{A}^\text{hy}_\text{IND-CCA}$, there exists an OW-CPA adversary $\mathcal{A}^\text{asym}_\text{OW-CPA}$ with advantage $\epsilon^\text{asym}_\text{OW-CPA}$ such that

    $$
    \epsilon^\text{asym}_\text{OW-CPA} = P[\text{query}] \cdot \frac{1}{q_H}
    $$

    where $q_H$ is the number of hash queries $\mathcal{A}^\text{hy}_\text{IND-CCA}$ makes to either $H$ or $G$.
\end{lemma}

\begin{proof}
    Similar to the proof of lemma \ref{fo-bound-s2}, $\mathcal{A}^\text{asym}_\text{OW-CPA}$ can perfectly simulate key generation, hash oracles, and decryption oracle.

    Let $e^\ast$ denote the asymmetric challenge ciphertext $\mathcal{A}^\text{asym}_\text{OW-CPA}$ receives from the OW-CPA challenger, let $\sigma^\ast$ denote the plaintext that corresponds with $e^\ast$, and let $(m_0, m_1)$ denote the challenge plaintexts submitted by $\mathcal{A}^\text{hy}_\text{IND-CCA}$. $\mathcal{A}^\text{asym}_\text{OW-CPA}$ samples a random symmetric key $a^\ast \leftsample \mathcal{K}^\text{sym}$ and a coin flip $b \leftsample \{0, 1\}$, then computes $c^\ast \leftarrow E^\text{sym}_{a^\ast}(m_b)$. $(e^\ast, c^\ast)$ is the IND-CCA challenge ciphertext.

    After the $\mathcal{A}^\text{hy}_\text{IND-CCA}$ halts, $\mathcal{A}^\text{asym}_\text{OW-CPA}$ looks through the tape of the hash oracles $\mathcal{O}^H = \{(\tilde{\sigma}, \tilde{c})\}$ and $\mathcal{O}^G = \{\tilde{\sigma}\}$, then picks a random value among all possible $\tilde{\sigma}$'s to output. $\mathcal{A}^\text{asym}_\text{OW-CPA}$ wins if $\mathcal{A}^\text{hy}_\text{OW-CPA}$ makes a query $\tilde{\sigma} = \sigma^\ast$ and the correct query is chosen.
\end{proof}

\section{Tweaking FO Transform for IND-CCA KEM}
While the FO transformation can construct IND-CCA public-key encryption scheme from OW-CPA PKE and IND-OTE symmetric cipher, there are a few drawbacks to the hybrid scheme as it is:

\begin{itemize}
    \item The security proof is not tight. The security of the hybrid scheme degrades linearly with the number of hash queries.
    \item The hybrid scheme assumes the underlying PKE to be always correct. This is not the case in PKEs such as schemes based on "Learning with Errors" (LWE), which can have a small but non-zero probability of decryption error
\end{itemize}

In 2017, Hofheinz et al \cite{hofheinz2017modular} improved the FO transformation by addressing the non-tight security and accounting for possible decryption errors. In addition, the paper proposed various IND-CCA KEM constructions from weak PKE's that does not require a symmetric cipher. In fact, both Kyber \cite{avanzi2019crystals} and Classic McEliece \cite{albrecht2022classic} make direct use of transformations proposed in this paper to achieve IND-CCA security for their respective KEMs.

The strategy for achieving IND-CCA KEM consists of two parts

\begin{itemize}
    \item Transform a OW-CPA and/or IND-CPA PKE into an OW-PCVA PKE
    \item Transform the OW-PCVA PKE into a IND-CCA KEM
\end{itemize}

The intermediary security definition PCVA is defined by two oracles: the \textbf{plaintext checking oracle (PCO)} and the \textbf{ciphertext validation oracle (CVO)}. The details of these two oracles will be discussed in the following section

\subsection{From OW/IND-CPA to OW-PCVA}
Let $(\text{KeyGen}, E, D)$ denote the input public-key encryption scheme, let $(\text{KeyGen}^T, E^T, D^T)$ denote the transformed public-key encryption scheme, let $G$ be a hash function. The transformed routines are as follows:

\begin{algorithm}
    \caption[keygen-t]{$\text{KeyGen}^T$}
    \begin{algorithmic}[1]
        \State $\text{pk}, \text{sk} \leftsample \text{KeyGen}()$
        \State \Return $\text{pk}^T \leftarrow \text{pk}, \text{sk}^T \leftarrow \text{sk}$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \caption[encrypt-t]{Encryption routine: $E^T$}
    \begin{algorithmic}[1]
        \Require The message $m \in \mathcal{M}$
        \State $r \leftarrow G(m)$ \Comment $r$ serves as the coin
        \State $c \leftarrow E(\text{pk}^T, m, r)$
        \State \Return $c$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \caption[decrypt-t]{Decryption routine: $D^T$}
    \begin{algorithmic}[1]
        \Require ciphertext $c \in \mathcal{C}$
        \State $\hat{m} \leftarrow D(\text{sk}, c)$
        \State $\hat{r} \leftarrow G(\hat{m})$
        \If{$E(\text{pk}, \hat{m}, \hat{r}) \neq c$}
            \State \Return $\bot$
        \EndIf
        \State \Return $\hat{m}$
    \end{algorithmic}
\end{algorithm}

To discuss the security of the transformed scheme, we first need to lay out the implementations of the PCO and the CVO. In the vanilla PCVA game, the two oracles have access to the challenge secret key and perform decryption routines:

>>>>

% Algorithms and pseudocode
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{multicol}

% Common shortcuts
\newcommand{\round}[1]{\lfloor {#1} \rceil}
\newcommand{\norm}[1]{\vert {#1} \vert}
\newcommand{\Norm}[1]{\Vert {#1} \Vert}
\newcommand{\var}[1]{\operatorname{Var}[{#1}]}
\newcommand{\leftsample}{\overset{{\scriptscriptstyle\$}}{\leftarrow}}

% Environments: definitions, theorems, propositions, corollaries, lemmas
%    Theorems, propositions, and definitions are numbered within the section
%    Corollaries are numbered within the theorem, though they are rarely used
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{remark}{Remark}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}

@@

\subsection{Spread and correctness}
The spread of measures the randomness of ciphertext in a probabilistic encryption scheme, where the randomness of the encryption routine is determined by a random coin $r \leftsample \text{Coin}$ from the coin space.

\begin{definition}[$\gamma$-spread]
    The spread $\gamma$ of an asymmetric encryption scheme $(\operatorname{KeyGen}, E, D)$ for some fixed public key $\text{pk}$ and plaintext $m$ is defined by

    \begin{equation*}
        \gamma(\text{pk}, m) = -\log{\Norm{E_\text{pk}(m)}_\infty}
    \end{equation*}

    Where $\Norm{E_\text{pk}(m)}_\infty$ is the min-entropy of the ciphertext with respect to the coin:

    \begin{equation*}
        \Norm{E_\text{pk}(m)}_\infty 
        = \max_{c \in \mathcal{C}} P[E_\text{pk}(m) = c]
    \end{equation*}
\end{definition}

\begin{definition}[correctness]
    A public-key encrpytion scheme $(\operatorname{KeyGen}, E, D)$ is $\delta$-correct if across all possible keypairs and messages, the probability of decryption error is at most $\delta$:

    \begin{equation*}
        \max_{
            m \in \mathcal{M},
            (\text{pk}, \text{sk}) \leftsample \operatorname{KeyGen}()
        } P[D_\text{sk}(E_\text{pk}(m)) \neq m]
        \leq \delta
    \end{equation*}
\end{definition}

\subsection{Difference lemma}
The difference lemma is used extensively in the sequence of games to estimate the loss of security when one game is transformed into another

\begin{lemma}[Difference lemma]
    Let $A, B, F$ be events defined on the same probability space. If $P[A \cap \neg F] = P[B \cap \neg F]$, then $P[A] - P[B] \leq P[F]$
\end{lemma}

\begin{proof}
    \begin{equation*}
        \begin{aligned}
            P[A] - P[B] &= (P[A \cap F] + P[A \cap \neg F]) 
                - (P[B \cap F] + P[B \cap \neg F]) \\
            &= (P[A \cap F] - P[B \cap F]) 
                + (P[A \cap \neg F] - P[B \cap \neg F]) \\
            &= P[A \cap F] - P[B \cap F] \\
            &\leq P[A \cap F] \\
            &\leq P[F]
        \end{aligned}
    \end{equation*}
\end{proof}

In the context of security reduction using sequence of game, the difference lemma is invoked with event $A$ and $B$ set to "adversary winning one game" and "adversary winning another game", and event $F$ set to the event that would cause the two games two diverge. If the diverging event $F$ does not happen, then the two games are identical to each other, so the advantage of the adversary remains the same across the two games; if the diverging event $F$ happens, then the advantage of the adversary does not change by more than the probability of the diverging event $F$.

\subsection{IND-CPA to OW-CPA}
It is trivially true that if a public-key encryption scheme is not one-way secure, then it is not indistinguishable. The converse if also almost true, with the caveat that the message space must be sufficiently large:

\begin{lemma}
    Let $(\operatorname{KeyGen}, E, D)$ be a public-key encryption scheme with a finite message space $\mathcal{M}$. For every IND-CPA adversary $A$, there exists an OW-CPA adversary $B$ such that

    \begin{equation*}
        \epsilon_\text{OW-CPA} = \epsilon_\text{IND-CPA} + \frac{1}{\norm{\mathcal{M}}}
    \end{equation*}
\end{lemma}

\section{Related works}
    Key encapsulation mechanisms (KEM) usually have weaker security requirements than public-key encryption schemes (PKE) thanks to the fact that properly designed KEMs obfuscate the plaintext through a key-derivation function (which is usually a hash function and thus a random oracle under the RO assumption) in the decryption routine. As a result, we can implement a simple IND-CCA2 KEM using an IND-CCA2 PKE:

    \begin{multicols}{3}
        \begin{algorithm}[H]
            \SetAlgoLined
            \caption{KeyGen}
            $(\text{pk}, \text{sk}) \leftsample \operatorname{KeyGen}()$ \;
            \Return{$(\text{pk}, \text{sk})$}
        \end{algorithm}

        \begin{algorithm}[H]
            \SetAlgoLined
            \caption{Encap}
            \KwIn{$\text{pk}$}
            $m \leftsample \mathcal{M}$\;
            $c \leftsample E(\text{pk}, m)$\;
            $K \leftarrow H(m, c)$\;
            \Return{$(c, K)$}\;
        \end{algorithm}

        \begin{algorithm}[H]
            \SetAlgoLined
            \caption{Decap}
            \KwIn{$\text{sk}, c \in \mathcal{C}$}
            $\hat{m} \leftarrow D(\text{sk}, c)$\;
            $\hat{K} \leftarrow H(\hat{m}, c)$\;
            \Return{$\hat{K}$}\;
        \end{algorithm}
    \end{multicols}

    It is straightforward to simulate the KEM game using a PKE adversary. The PKE adversary samples two random messages $(m_0, m_1) \leftsample \mathcal{M}$ and obtains the challenge encryption for one of them $c^\ast \leftarrow E(\text{pk}, m_b)$. The PKE adversary then computes $K^\ast \leftarrow H(c^\ast, m_0)$ and passes $(c^\ast, K^\ast)$ as the challenge encapsulation to the KEM adversary. If $c^\ast$ is an encryption of $m_0$, then $K^\ast$ is pseudorandom, otherwise under the random oralce model, $K^\ast$ is truly random from the perspective of the KEM adversary. Therefore, $\epsilon_\text{PKE} = \epsilon_\text{KEM}$.

    Using IND-CCA2 PKE as an IND-CCA2 KEM has been in production for a long time. For example, TLS 1.2 \cite{dierks2008rfc} offers this implementation for key exchange using RSA-OAEP\cite{bellare1995optimal} as the underlying IND-CCA2 PKE. The key exchange protocol proceeds as follows:

    \begin{enumerate}
        \item Server sends its public key through the X.509 certificate
        \item Client samples a master secret, encrypts the secret using server's public key, then sends the ciphertext to the server
        \item Server decrypts the ciphertext to obtain the master secret
    \end{enumerate}

    This approach to key exchange has since been deprecated, and RSA is no longer supported for key exchange starting with TLS 1.3. In addition to the difficulty of implementing RSA correctly and securely (RSA is notoriously hard to implement without side-channel vulnerabilities), using the server's long-term keypair for establishing common secrets fails to provide forward secrecy, meaning that if the long-term key is compromised, all prior communications can be trivially decrypted.

    While the modern approach is to use ephemeral Diffie-Hellman (with either prime field or elliptic curve), it is difficult to adapt this approach to the post-quantum setting. Instead, post-quantum key exchange usually builds an IND-CCA2 KEM, then perform the key exchange using ephemeral keypairs. At each session's handshake, the client generates the a new keypair and sends the public key to the server. The server uses the public key to run the encapsulation routine and sends back the ciphertext. Finally, the client runs the decapsulation routine on the ciphertext to recover the shared secret.

\section{Fujisaki-Okamoto transformation and variations}
In 1999, Fujisaki and Okamoto \cite{fujisaki1999secure} proposed a generic transformation that outputs an IND-CCA2-secure public-key encryption scheme using an IND-CPA symmetric cipher, an OW-CPA asymmetric cipher, and two hash functions. Later on in 2017, Hofheinz, Hovelmann, and Kiltz \cite{hofheinz2017modular} improved on the security of the Fujisaki-Transformation and adapted the original approach to constructing IND-CCA2 KEMs. In this section, we will give a quick overview of the individual transformations and their security results. We will then discuss the techniques used in the security reduction. Finally, we will provide a sketch of the actual proof.

\subsection{An overview of transformed routines and security results}
The original 1999 Fujisaki-Okamoto transformation takes as input a symmetric cipher $(E^\text{sym}, D^\text{sym})$, an asymmetric cipher $(\operatorname{KeyGen}, E^\text{asym}, D^\text{asym})$, a key derivation function (aka a hash function) $G: \mathcal{M}^\text{asym} \rightarrow \mathcal{K}^\text{sym}$, and a hash functino $H: \{0, 1\}^\ast \rightarrow \text{Coin}^\text{asym}$.

Specifically, the asymmetric cipher is assumed to be probabilistic, but with pseudorandomness seeded on some coin $r \in \text{Coin}^\text{asym}$. When $E^\text{asym}$ is called without specifying a value for coin, it is assumed that a coin is uniformly sampled from the coin space and passed in as the pseudorandom seed:

$$
    c \leftsample E^\text{asym}(\text{pk}, m) 
    \Leftrightarrow 
    c \leftarrow E^\text{asym}(\text{pk}, m, r \leftsample \text{Coin})
$$

The output of the transformation is a public-key encryption scheme $(\operatorname{KeyGen}, E^\text{hy}, D^\text{hy})$. Note that the key generation routine is exactly the same as the input asymmetric cipher's routine, so no distinction of notation is needed. The encryption and decryption routines are as follows:

\begin{multicols}{2}
    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{Hybrid encryption $E^\text{hy}$}
        \KwIn{$\text{pk}, m \in \mathcal{M}^\text{sym}$}
        $\sigma \leftsample \mathcal{M}^\text{asym}$\;
        $a \leftarrow G(\sigma)$; $c \leftarrow E^\text{sym}_a(m)$\;
        $r \leftarrow H(\sigma, c)$;
        $e \leftarrow E^\text{asym}(\text{pk}, m, r)$\;
        \Return{$(c, e)$}\;
    \end{algorithm}

    \columnbreak

    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{Hybrid decryption $D^\text{hy}$}
        \KwIn{$\text{sk}, c \in \mathcal{C}^\text{sym}, e \in \mathcal{C}^\text{asym}$}
        $\hat{\sigma} \leftarrow D^\text{asym}(\text{sk}, e)$\;
        $\hat{r} \leftarrow H(\hat{\sigma}, c)$\;
        \If{
            $E^\text{asym}(\text{pk}, \hat{\sigma}, \hat{r}) \neq e$
        }{
            \Return{$\bot$}; \tcp*[h]{the "re-encryption"}
        }
        $\hat{a} \leftarrow G(\hat{\sigma})$\;
        $\hat{m} \leftarrow D^\text{sym}_{\hat{a}}(c)$\;
        \Return{$\hat{m}$}\;
    \end{algorithm}
\end{multicols}

\begin{theorem}[Security result for $(E^\text{hy}, D^\text{hy})$]
    If the input asymmetric cipher has $\gamma$ spread, then for every IND-CPA adversary $\mathcal{A}^\text{sym}_\text{IND-CPA}$ against the underlying symmetric cipher with advantage $\epsilon^\text{sym}$ and OW-CPA adversary $\mathcal{A}^\text{asym}_\text{OW-CPA}$ against the input asymmetric cipher with advantage $\epsilon^\text{asym}$, there exists an IND-CCA2 adversary with against the hybrid scheme making $q_H$ hash queries and $q_D$ decryption queries such that:

    \begin{equation*}
        \epsilon^\text{hy} 
        \leq q_D2^{-\gamma} 
            + \epsilon^\text{sym} 
            + q_H\epsilon^\text{asym}
    \end{equation*}
\end{theorem}

Hofheinz, Hovenmann, and Kiltz pointed out in their 2017 paper a number of drawbacks of the original FO transformation:

\begin{enumerate}
    \item Decryption error, which is especially possible with lattice-based schemes, is not accounted for
    \item the $q_H\epsilon^\text{asym}$ term causes security to be non-tight, which have implications when choosing the security parameters
\end{enumerate}

In their proposals, IND-CCA2 security is achieved through a two-step transformation. First, an OW-CPA asymmetric scheme is transformed into an OW-PCVA asymmetric scheme. The OW-PCVA scheme is then transformed into an IND-CCA2 KEM. Here PCVA refers to the adversary's ability to access some plaintext-checking oracle and some ciphertext validation oracle. Although PCVA is a non-standard security definition, it is entirely contained within the two-step transformation and serves only as an intermediary step.

Neither the OW-PCVA nor the IND-CCA transformation makes use of any symmetric cipher, so we ditch the distinction. The OW-PCVA transformation takes as input an asymmetric cipher $(E, D)$ and a hash function $G: \mathcal{M} \rightarrow \text{Coin}$. The transformed encryption and decryption routines $(E^T, D^T)$ are as follows:

\begin{multicols}{2}
    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{OW-PCVA $E^T$}
        \KwIn{$\text{pk}, m \in \mathcal{M}$}
        $r \leftarrow G(m)$\;
        $c \leftarrow E(\text{pk}, m, r)$\;
        \Return{$c$}\;
    \end{algorithm}

    \columnbreak

    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{OW-PCVA $D^T$}
        \KwIn{$\text{sk}, c \in \mathcal{C}$}
        $\hat{m} \leftarrow D(\text{sk}, c)$\;
        $\hat{r} \leftarrow G(\hat{m})$\;
        \If{
            $E(\text{pk}, \hat{m}, \hat{r}) \neq c$
        }{
            \Return{$\bot$}\;
        }
        \Return{$\hat{m}$};
    \end{algorithm}
\end{multicols}

Depending on whether the implementation chooses implicit or explicit rejection of invalid ciphertext for the final KEM, the second transformation has slightly different key generation and decryption routine. The explicit rejection KEM is denoted by $U^\bot$, and its key generation is identical to the input asymmetric cipher.

\begin{multicols}{2}
    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{$U^\bot$ Encap}
        \KwIn{$\text{pk}$}
        $m \leftsample \mathcal{M}$\;
        $c \leftarrow E^T(\text{pk}, m)$\;
        $K \leftarrow H(m, c)$ \tcp*[h]{H is a hash function}\;
        \Return{$(c, K)$}
    \end{algorithm}
    \columnbreak

    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{$U^\bot$ Decap}
        \KwIn{$c \in \mathcal{C}, \text{sk}$}
        $\hat{m} \leftarrow D^T(\text{sk}, c)$\;
        \If{
            $m = \bot$
        }{
            \Return{$\bot$};
        }
        \Return{$H(\hat{m}, c)$}
    \end{algorithm}
\end{multicols}

On the other hand, the implicit rejection KEM, denoted by $U^{\not\bot}$, generate a random message $m^\prime \leftsample \mathcal{M}$ as the fake input to $H$ when the ciphertext is invalid

\begin{multicols}{3}
    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{KeyGen}
        $\text{pk}, \text{sk} \leftsample \operatorname{KeyGen}()$\;
        $m^\prime \leftsample \mathcal{M}$\;
        \Return{$(\text{pk}, (\text{sk}, m^\prime))$}\;
    \end{algorithm}
    \columnbreak

    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{Encap}
        $m \leftsample \mathcal{M}$\;
        $c \leftarrow E^T(\text{pk}, m)$\;
        $K \leftarrow H(m, c)$\;
        \Return{$(c, K)$}
    \end{algorithm}
    \columnbreak

    \begin{algorithm}[H]
        \SetAlgoLined
        \caption{Decap}
        $\hat{m} \leftarrow D^T(\text{sk}, c)$\;
        \If{
            $m = \bot$
        }{
            \Return{$H(m^\prime, c)$};
        }
        \Return{$H(\hat{m}, c)$}
    \end{algorithm}
\end{multicols}

The security result is similarly expressed in two theorems:

\begin{theorem}
    If the input asymmetric scheme is $\delta$-correct and $\gamma$-spread, then for every OW-PCVA adversary that issues at most $q_G$ hash queries and $q_V$ ciphertext validation queries with advantage $\epsilon^T$, there exists an IND-CPA adversary against the underlying asymmetric scheme with advantage $\epsilon$ such that

    \begin{equation*}
        \epsilon^T \leq q_G \cdot \delta + q_V \cdot 2^{-\gamma} 
            + \frac{2q_G + 1}{\norm{\mathcal{M}}}
            + 3\epsilon
    \end{equation*}
\end{theorem}

\begin{theorem}
    For every IND-CCA2 adversary against the $U^\bot$ KEM with advantage $\epsilon^{U^\bot}$, there exists an OW-PCVA adversary against the input scheme $(E^T, D^T)$ with advantage $\epsilon^T$ such that

    \begin{equation*}
        \epsilon^{U^\bot} \leq \epsilon^T
    \end{equation*}
\end{theorem}

\begin{theorem}
    For every IND-CCA2 adversary against the $U^{\not\bot}$ KEM that issues $q_H$ hash queries with advantage $\epsilon^{U^{\not\bot}}$, there exists an OW-PCVA adversary against the input scheme $(E^T, D^T)$ with advantage $\epsilon^T$ such that

    \begin{equation*}
        \epsilon^{U^{\not\bot}} \leq \epsilon^T + \frac{q_H}{\norm{\mathcal{M}}}
    \end{equation*}
\end{theorem}

\subsection{A discussion of techniques}

\subsection{A sketch of proof}

\section{Future works on generic IND-CCA transformation}
